---
title: "2.5 Encapsulating the Framework"
output: html_notebook
---

This is an attempt to create an S3 class called **pmf**.

need a

- contructor, new_pmf()
- validator, validate_pmf()
- helper, pmf()

in S3 a class is a base type (e.g. vector, list) with the class attribute set.

My initial decision is that pmf will be a named double-precision vector .

```{r normalize}
normalize <- function(x) {
  #ensure  the values in the vector x add up to one
  x /sum(x)
  }
```
```{r mult}
mult <- function(prior,hypo,likelihood){
  prior[hypo] * likelihood
}
```

```{r update}
#Updates each hypothesis based on the data
update <- function(pmf, data){
    likelihoods <- vapply(names(pmf),likelihood, c(like = 0.0), data = data) 
    pmf <- mapply(mult,
                  hypo = names(pmf),
                  likelihood = likelihoods,
                  MoreArgs = list(prior = pmf),
                  USE.NAMES = FALSE) 
    normalize(pmf)
    }
```




```{r pmf constructor}
new_pmf <- function(hypos) {
# Represents a a probability mass function.
# return a named numeric vector of equal probabilities
# from a character vector of hypotheses, with class pmf   
       
      l <- length(hypos)
      pmf <- rep(1,l)
      names(pmf) <- hypos
      pmf <- normalize(pmf)
      structure(pmf, class = "pmf")
}

```
```{r pmf validator}
validate_pmf <- function(x){
  #more complex checking logic
  #check all names are unique
  if (anyDuplicated(names(x)) > 0) {
    stop(
      "All hypotheses must be unique",
      call. = FALSE
    )
  
  }
  x
}
```

```{r pmf helper}
pmf <- function(hypos) {
  validate_pmf(new_pmf(hypos))
}
```

The class defined above will be helpful in the futue but could be replaced by just functions.
Initial thoughts are that all that differs is the likelihood function for each class . Maybe I can just use S3 generics


```{r likelihood generic}
likelihood <- function(data, hypo, ...){
  UseMethod("likelihood")
}
```

```{r monty class}
#Constructor
new_monty <- function(x) {
# a character vector of class monty   
      stopifnot(is.character(x))
      structure(x, class = "monty")
}
#Validator
validate_monty <- function(x){
  #complicated checks go here i.e. must be A, B or C
  x
}
#helper
monty <- function(door = "B"){
  #public facing , todo: helpful errors
  validate_monty(new_monty(door))
}
```
```{r}
likelihood.monty <- function(data, hypo){
    if (hypo == data) {
      0
    } else if (hypo == "A") {
      0.5
    } else {
      1
    }
  
}
```







```{r main}
hypos  <-  LETTERS[1:3]

monty_pmf <- pmf(hypos)

data <- monty()

monty_pmf <- update(monty_pmf, data)

monty_pmf
```





