---
title: "The M & M  problem"
output: html_notebook
---

```{r normalize}
normalize <- function(x) {
  #ensure  the values in the vector x add up to one
  x /sum(x)
  }
```
```{r mult}
mult <- function(prior,hypo,likelihood){
  prior[hypo] * likelihood
}
```

```{r update}
#Updates each hypothesis based on the data
update <- function(pmf, data){
    likelihoods <- vapply(names(pmf),likelihood, c(like = 0.0), data = data) 
    pmf <- mapply(mult,
                  hypo = names(pmf),
                  likelihood = likelihoods,
                  MoreArgs = list(prior = pmf),
                  USE.NAMES = FALSE) 
    normalize(pmf)
    }
```




```{r pmf constructor}
new_pmf <- function(hypos) {
# Represents a a probability mass function.
# return a named numeric vector of equal probabilities
# from a character vector of hypotheses, with class pmf   
       
      l <- length(hypos)
      pmf <- rep(1,l)
      names(pmf) <- hypos
      pmf <- normalize(pmf)
      structure(pmf, class = "pmf")
}

```
```{r pmf validator}
validate_pmf <- function(x){
  #more complex checking logic
  #check all names are unique
  if (anyDuplicated(names(x)) > 0) {
    stop(
      "All hypotheses must be unique",
      call. = FALSE
    )
  
  }
  x
}
```

```{r pmf helper}
pmf <- function(hypos) {
  validate_pmf(new_pmf(hypos))
}
```

The class defined above will be helpful in the futue but could be replaced by just functions.
Initial thoughts are that all that differs is the likelihood function for each class . Maybe I can just use S3 generics


```{r likelihood generic}
likelihood <- function(data, hypo, ...){
  UseMethod("likelihood")
}
```

```{r m_and_m class}
#Constructor
m_and_m_new <- function(x) {
# a character vector of class monty   
      stopifnot(is.character(x))
      structure(x, class = "m_and_m")
}
#Validator
validate_m_and_m <- function(x){
  #complicated checks go here i.e. 
  x
}
#helper
m_and_m <- function(data){
  #public facing , todo: helpful errors
  validate_m_and_m(m_and_m_new(data))
}
likelihood.m_and_m <- local({
  #this is a technique known as memoizaiton. using global assignment (the <<- operator ) in this local namespace.
  
  
  mix94 <- c(brown=30,
                 yellow=20,
                 red=20,
                 green=10,
                 orange=10,
                 tan=10)
  mix96 <-  c(blue=24,
                 green=20,
                 orange=16,
                 yellow=14,
                 red=13,
                 brown=13)
 hypoA  <-  list(bag1=mix94, bag2=mix96)
 hypoB <- list(bag1=mix96, bag2=mix94)
 hypotheses  <-  list(A=hypoA, B=hypoB)
  
  
  function(data, hypo){
  bag <- data[1]
  color <- data[2]
  mix <- hypotheses[[hypo]][[bag]]
  mix[color]
  
  
  }
})

```
Decided to use used memoization to encapsulate the encoding of color mixes and mapping of hypothesis name to representation all within the **likelihood.m_and_m method.**
This approach all existing functions and methods remain unchanged and I didn't have to refer to objects I had created in "main".


```{r main}
#see the objects in the environment of the likelihood.m_and_m function
objects(envir = environment(likelihood.m_and_m))
hypos  <-  c("A","B")


M_and_M_pmf <- pmf(hypos)

data <- m_and_m(c("bag1","yellow"))

M_and_M_pmf <- update(M_and_M_pmf, data)

data <- m_and_m(c("bag2","green"))

M_and_M_pmf <- update(M_and_M_pmf, data)

M_and_M_pmf

 
```
